---
title: "Meeting-02 Meeting Notebook"
author: "Christopher Prener, Ph.D."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
always_allow_html: yes
---

## Introduction
This notebook provides a walk-through of the example code used in class.

## Dependencies
This notebook requires the following packages:

```{r load-packages}
# tidyverse packages
library(ggplot2)       # static mapping

# mapping packages
library(mapview)      # preview spatial data
library(sf)           # spatial tools

# other packages
library(here)         # file path management
library(viridis)      # viridis color palettes
```

## Load Data
The data for today's lecture are county-level population estimates from the 2010 Decennial Census for California. These can be found in `data/CA_DEMOS_Total_Population`. They are shapefile data:

```{r load-data}

```

## Map 1 - Total Population
The first map we'll make will be incorrect cartographically, but it will give us a chance to practice mapping just a bit with `ggplot2`. We'll use a number of functions to build our map:

  1. `ggplot()` creates an empty `ggplot2` object for producing plots and maps
  2. `geom_sf()` draws the geometric data, and we *map* the *fill* to the `total_pop` column
  3. `scale_fill_viridis()` applies the viridis color palette to our map, and we can use the `name` argument to add a title to the legend
  4. `labs()` is used to make annotations on our map layout, which can include a title, subtitle, and caption
  
Notice how we use the `+` sign to chain our functions together. This works rather like the `%>%` operator we used last time, but it is notation that is specific to `ggplot2`.

We've discussed the concept of "layers" already during this meeting. This map has one layer - the county boundaries filled with their total population.

```{r, map-1}

```

We've now stored our map in the `p1` object so that we can reference it later. One way we use this is to save it, using the `ggsave()` function:

```{r, save-map-1}
ggsave(plot = p1, filename = here("results", "ex_ca_total_population.png"))
```

Now our map has been saved!

## Map 2 - Population Density
The map above is not correct cartographically because it isn't *normalized*. There are three ways we can normalize data:

  1. We can show density by dividing our value by the area of the unit it falls into, such as the square kilometers of each county
  2. We can show percent of total by dividing our value by the total population and multiplying it by 100. This doesn't make a whole lot of sense with total population, but if you had the number of women in each county, for example, it would work.
  3. We can show per capita rates by dividing our value by the total population and multiplying it by 1,000 or 10,000 or 100,000 or even 1,000,000. The denominator depends on how big our areal unit's total population is and how common our value is as well. So, we could map the number of women per 1,000 residents of a county, for example.

Since mapping density is really the only option for us with these data, we'll go ahead and re-create our map from above, except we'll use the `pop_den` column:

```{r, map-2}

```

We've now stored our map in the `p2` object so that we can reference it later. One way we use this is to save it, using the `ggsave()` function:

```{r, save-map-2}

```

Now our second map has been saved!
