\documentclass{tufte-handout}

\usepackage{xcolor}

% set image attributes:
\usepackage{graphicx}
\graphicspath{ {images/} }

% set hyperlink attributes
\hypersetup{colorlinks}

% set table attributes
\usepackage{tabu}
\usepackage{booktabs}

% set list attributes:
\usepackage{enumerate}
\usepackage{enumitem}

% =======================================================

% define the title
\title{SOC 4650/5650: Lab-01 - Introduction to ArcGIS }
\author{Christopher Prener, Ph.D.}
\date{Spring 2019}
% ======================================================
\begin{document}
% =======================================================
\maketitle % generates the title
% =======================================================

\vspace{5mm}
\section{Directions}
Complete all of the following questions using the data from the \texttt{lecture-02} repository on GitHub. You'll be making a map of fire station locations in the City of St. Louis. Your ArcGIS Project, including map output, should be \textit{ready} to be uploaded to your assignments repository by 4:15pm on Monday, January 28\textsuperscript{th}, 2019. We'll go through the submission itself together as a class.

\vspace{5mm}
\section{Analysis Development}
\subsection{Download Data}
\begin{enumerate}[label=\alph*.]
\item Download the \texttt{lecture-02} repository from GitHub - there is a \textsf{green button} that reads \textsf{Clone or download} that is visible in the repo. \textsf{Click} on it and then choose \textsf{Download ZIP}.
\item Extract the \texttt{.zip} file if necessary and save it to your Desktop.
\end{enumerate}

\vspace{3mm}
\subsection{Create a Project Folder System}
\begin{enumerate}[label=\alph*.]
\setcounter{enumi}{2}
\item Open ArcGIS Pro and choose \textsf{Blank} under \textsf{Create a new project}. Name the project \texttt{Lab-01} and save it to your Desktop.
\item Reduce ArcGIS Pro for a moment. On the Windows File Explorer app, drag the \texttt{data/} folder within \texttt{lecture-02} into the \texttt{Lab-01} project.
\item In ArcGIS Pro, click on \textsf{Folders} in the \textsf{Contents} pane. In the center \textsf{Catalog} window, \textsf{double-click} on \texttt{Lab-01} and verify that the \texttt{data/} folder is visible. If it is not, you may need to re-start ArcGIS Pro and/or verify that you moved the data to the correct location.
\end{enumerate}

\vspace{5mm}
\section{Part 1: Create Map}
\begin{enumerate}
\item In the \textsf{Catalog} pane, \textsf{double-click} on the \textsf{data/} folder and again on \textsf{STL\_BOUNDARY\_City}. \textsf{Right-click} on \texttt{STL\_BOUNDARY\_City.shp} and choose \textsf{Add To New Map}.
\item Once the map loads, \textsf{right-click} on the \texttt{STL\_BOUNDARY\_City} entry in the \textsf{Contents} pane on the left side of the screen and choose \textsf{Symbology}. 
\item In the \textsf{Symbology} pane, \textsf{click} on the color swatch and choose the middle \textsf{Black Outline} option.
\item Change the basemap to a different basemap of your choosing.\sidenote{\textit{Hint:} The \textsf{Basemap} button in the \textsf{Map} ribbon. This was discussed in the reading for this week!}
\item Click on \textsf{Add Data} in the \textsf{Map} ribbon, choose \textsf{Data} and then click through \texttt{Folders} $\triangleright$ \texttt{Lab-01} $\triangleright$ \texttt{data} $\triangleright$ \texttt{PublicSaftey.gdb} and choose the \textsf{STL\_PUBLICSAFTEY\_FireStations} data.
\item Change the symbology of the fire stations layer.\sidenote{\textit{Hint:} See page 27.}
\item Select the fire stations layer again if necessary, and then the \textsf{Labeling} ribbon. Enable labeling\sidenote{\textit{Hint:} See pages 28-29.} Then, under the \textsf{Field} dropdown, choose the \texttt{stationID} variable. 
\item Switch tot he \texttt{Share} ribbon and select \textsf{Export}. Change the \textsf{Save as type} dropdown to \texttt{.png}. Choose the \texttt{Lab-01} project folder and then \textsf{right-click} and select \textsf{New} $\triangleright$ \textsf{Folder}. Name the new folder \texttt{results}. Save your map in this new \texttt{results} folder as \texttt{lab-01-map.png}. Click \textsf{Export}.
\item Close ArcGIS Pro, and opt to save changes to your project if prompted.
\end{enumerate}

\vspace{5mm}
\section{Reminders}
Remember that a replication file will be posted on GitHub and linked to from the course website.

% ============================================================
\end{document}